---
title: "Potential Figures for Paper"
author: "Loecher+Lai"
date: "15/12/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggstatsplot)
library(ggplot2)
library(plyr)
library(scales)
setwd("/Users/aubrey/Documents/GitHub/ExplainableAI/ConferenceSubmission")
getwd()

```


## Predictive Power of Feature Subsets

### Random Forests

```{r}
corr_shap_ti_rmse <- read.csv("Data/ti&shap_resample/corr_shap_ti_rmse_p.csv")
corr_shap_ti_nloss <- read.csv("Data/ti&shap_resample/corr_shap_ti_nloss.csv")

# Rescale to nloss
corr_shap_ti_rmse$perform <- (corr_shap_ti_rmse$perform-min(corr_shap_ti_rmse$perform))/(max(corr_shap_ti_rmse$perform)-min(corr_shap_ti_rmse$perform))*max(corr_shap_ti_nloss$perform)
#  rescale(corr_shap_ti_rmse$perform,
#                                    from = min(corr_shap_ti_nloss$perform),
#                                    to = max(corr_shap_ti_nloss$perform))

# Combine
corr_shap_ti_rmse["type"] <- "Regression"
corr_shap_ti_nloss["type"] <- "Classification"
data <- rbind(corr_shap_ti_rmse,corr_shap_ti_nloss)
#corr_shap_ti_f1 <- read.csv("data/corr_shap_ti_f1.csv")
```

Adjusted ggscatterstats() function
```{r}
myggscatterstats <- function(data,
                             x,
                             y,
                             type = "parametric",
                             conf.level = 0.95,
                             bf.prior = 0.707,
                             bf.message = TRUE,
                             tr = 0.2,
                             k = 2L,
                             results.subtitle = TRUE,
                             label.var = NULL,
                             label.expression = NULL,
                             marginal = TRUE,
                             xfill = "#009E73",
                             yfill = "#D55E00",
                             point.args = list(
                               size = 3,
                               alpha = 0.4,
                               stroke = 0,
                               na.rm = TRUE
                             ),
                             point.width.jitter = 0,
                             point.height.jitter = 0,
                             point.label.args = list(size = 3, max.overlaps = 1e6),
                             smooth.line.args = list(
                               size = 1.5,
                               color = "blue",
                               method = "lm",
                               formula = y ~ x,
                               na.rm = TRUE
                             ),
                             xsidehistogram.args = list(
                               fill = xfill,
                               color = "black",
                               na.rm = TRUE
                             ),
                             ysidehistogram.args = list(
                               fill = yfill,
                               color = "black",
                               na.rm = TRUE
                             ),
                             xlab = NULL,
                             ylab = NULL,
                             title = NULL,
                             subtitle = NULL,
                             caption = NULL,
                             ggtheme = ggstatsplot::theme_ggstatsplot(),
                             ggplot.component = NULL,
                             output = "plot") {
  
  # data ---------------------------------------
  
  # ensure the arguments work quoted or unquoted
  c(x, y) %<-% c(ensym(x), ensym(y))
  
  # preparing the dataframe
  # data %<>% filter(!is.na({{x}}), !is.na({{y}}))
  
  # statistical analysis ------------------------------------------
  
  # adding a subtitle with statistical results
  if (results.subtitle) {
    # convert entered stats type to a standard notation
    type <- stats_type_switch(type)
    
    # relevant arguments for statistical tests
    .f.args <- list(
      data = data,
      x = {{ x }},
      y = {{ y }},
      conf.level = conf.level,
      k = k,
      tr = tr,
      bf.prior = bf.prior,
      top.text = caption
    )
    
    subtitle_df <- eval_f(corr_test, !!!.f.args, type = type)
    subtitle <- if (!is.null(subtitle_df)) subtitle_df$expression[[1]]
    
    # preparing the BF message for null hypothesis support
    if (type == "parametric" && bf.message) {
      caption_df <- eval_f(corr_test, !!!.f.args, type = "bayes")
      caption <- if (!is.null(caption_df)) caption_df$expression[[1]]
    }
  }
  
  # quit early if only subtitle is needed
  if (output != "plot") {
    return(switch(output,
                  "caption" = caption,
                  subtitle
    ))
  }
  
  # plot ------------------------------------------
  
  # creating jittered positions
  pos <- position_jitter(width = point.width.jitter, height = point.height.jitter)
  
  # preparing the scatterplot
  plot <- ggplot(data, mapping = aes({{ x }}, {{ y }})) +
    exec(geom_point, position = pos, !!!point.args) +
    exec(geom_smooth, level = conf.level, !!!smooth.line.args)
  
  # annotations -------------------------------------
  
  plot <- plot +
    labs(
      x = xlab %||% as_name(x),
      y = ylab %||% as_name(y),
      title = title,
      subtitle = subtitle,
      caption = caption
    ) +
    ggtheme +
    ggplot.component
  
  # marginal  ---------------------------------------------
  
  if (marginal) {
    # installed?
    #check_if_installed("ggside", minimum_version = "0.1.2")
    
    # adding marginal distributions
    plot <- plot +
      exec(ggside::geom_xsidehistogram, mapping = aes(y = after_stat(count)), !!!xsidehistogram.args) +
      exec(ggside::geom_ysidehistogram, mapping = aes(x = after_stat(count)), !!!ysidehistogram.args) +
      #labs(x = NULL, y = NULL)
      ggside::scale_ysidex_continuous(limits = NULL,n.breaks = NULL,
                                      labels = NULL) +
                                      # guide = guide_axis(angle = 90)) +
      ggside::scale_xsidey_continuous(limits = NULL,n.breaks = NULL,
                                      labels = NULL) +
                                      # guide = guide_axis(angle = 90)) +
      ggplot2::theme(axis.ticks.x=element_blank(),axis.ticks.y=element_blank())
      #                axis.ticks.x=element_blank(),
      #                axis.text.y=element_blank(),
      #                axis.ticks.y=element_blank())
  }
  
  # return the final plot
  plot
}
```


```{r}
p1 = myggscatterstats(
    data = data,
    x = corr_ti,
    y = corr_shap,
    xlab = "SHAP",
    ylab = "CFC",
    #ysidehistogram.args = list(ggplot2::theme(axis.text.x=element_blank())),
    bf.message = FALSE,
    #grouping.var = "type",
    #colour = "col",
    #palette = c("#00AFBB", "#E7B800"),
    results.subtitle = FALSE,
    smooth.line.args = list(size = 0.25, color = "blue"),
    point.args = list(size = 2, alpha = 0.4, stroke = 0),
    title = "Predictive Power (Log Loss) of Feature Subsets",
    ggplot.component = list(ggplot2::geom_point(aes(colour = perform,
                                                    shape = type)))
                            #ggplot2::theme(axis.ticks=element_blank()))
                            # ggplot2::guides(colour = guide_colourbar(order = 1),
                            # alpha = guide_legend(legend.position ="bottom",order = 2),
                            # shape = guide_legend(order = 3)),
                            # ggplot2::scale_alpha(guide = "legend"),
                            # ggplot2::scale_colour_continuous(guide = "legend"),
                            #ggplot2::scale_shape(guide = "legend"))
)


ggsave("Figures/PredictiveLoss_LL.pdf",p1, width=6, height=4)
p1

```

I rescale the range of rmse to that of nloss.

The Logloss/rmse is almost small because the points are mostly light and the correlations between perform and ti/shap is mostly gather at the left bottom.
The higher important one feature is used during prediction, the lower the Logloss/rmse.

## Arranging on grid

```{r}
# colnames(corr_shap_ti_mse)[4] = "LL"
# p1a = ggscatterstats(
#     data = corr_shap_ti_mse,
#     x = corr_ti,
#     y = corr_shap,
#     xlab = "SHAP",
#     ylab = "CFC",
#     bf.message = FALSE,
#     results.subtitle = FALSE,
#     smooth.line.args = list(size = 0.25, color = "blue"),
#     point.args = list(size = 2, alpha = 0.4, stroke = 0),
#     title = "MSE", ggplot.component = list(ggplot2::geom_point(aes(color = LL)), ggplot2::theme(legend.position = c(0.85, 0.3)))
# )
# 
# colnames(corr_shap_ti_f1)[4] = "F1"
# p2a =ggscatterstats(
#     data = corr_shap_ti_f1,
#     x = corr_ti,
#     y = corr_shap,
#     xlab = "SHAP",
#     ylab = "CFC",
#     bf.message = FALSE,
#     results.subtitle = FALSE,
#     smooth.line.args = list(size = 0.25, color = "blue"),
#     point.args = list(size = 2, alpha = 0.4, stroke = 0),
#     title = "F1 score", ggplot.component = list(ggplot2::geom_point(aes(color = F1)), ggplot2::theme(legend.position = c(0.85, 0.3)))
# )


```



```{r}
#ggpubr::ggarrange(p1,p2)

# library(grid)
# library(gridExtra)
# #p12 = grid.arrange(p1a, p2a, ncol=2, nrow=1,
# p12 = grid.arrange(p1a, ncol=2, nrow=1,
#      top = textGrob("Predictive Power of Feature Subsets",gp=gpar(fontsize=12,font=3)))
# 
# ggsave("figures/Predictive_MSE_both.pdf",p12, width=8, height=4)
```

```{r}
#ggpubr::ggarrange(p1,p2)

# p12 = grid.arrange(p1a, p2a, ncol=1, nrow=2,
#      top = textGrob("Predictive Power of Feature Subsets",gp=gpar(fontsize=12,font=3)))
# 
# ggsave("figures/PredictiveLoss_2x1.pdf",p12, width=4, height=6)
```


### Boosting

```{r}
# corr_shap_ti_nloss <- read.csv("data/boosting_corr_shap_ti_nloss.csv")
# 
# corr_shap_ti_f1 <- read.csv("data/boosting_corr_shap_ti_f1.csv")
```

```{r}
# colnames(corr_shap_ti_nloss)[4] = "LL"
# p1a = ggscatterstats(
#     data = corr_shap_ti_nloss,
#     x = corr_ti,
#     y = corr_shap,
#     xlab = "SHAP",
#     ylab = "CFC",
#     bf.message = FALSE,
#     results.subtitle = FALSE,
#     smooth.line.args = list(size = 0.25, color = "blue"),
#     point.args = list(size = 2, alpha = 0.4, stroke = 0),
#     title = "Log Loss", ggplot.component = list(ggplot2::geom_point(aes(color = LL)), ggplot2::theme(legend.position = c(0.85, 0.3)))
# )
# 
# colnames(corr_shap_ti_f1)[4] = "F1"
# p2a =ggscatterstats(
#     data = corr_shap_ti_f1,
#     x = corr_ti,
#     y = corr_shap,
#     xlab = "SHAP",
#     ylab = "CFC",
#     bf.message = FALSE,
#     results.subtitle = FALSE,
#     smooth.line.args = list(size = 0.25, color = "blue"),
#     point.args = list(size = 2, alpha = 0.4, stroke = 0),
#     title = "F1 score", ggplot.component = list(ggplot2::geom_point(aes(color = F1)), ggplot2::theme(legend.position = c(0.85, 0.3)))
# )
# 
# p12 = grid.arrange(p1a, p2a, ncol=1, nrow=2,
#      top = textGrob("Predictive Power of Feature Subsets",gp=gpar(fontsize=12,font=3)))
# 
# p12
# ggsave("figures/PredictiveLoss_2x1_boosting.pdf",p12, width=4, height=6)
```
```
